### 2023-03-29 Documentation/WT group/NHL/Results/Results.tex
documentation

@@

\begin{figure}[H]
    \center
    \includegraphics[width=17cm]{Figuras/report3/screenshots/stableConeExp.png}
    \caption{running experiment print screen}
\end{figure}

@@

@@

\begin{figure}[H]
    \center
    \includegraphics[width=18cm]{Figuras/19:03/control_first_results.png}
    \caption{ exp-26-01-2 (V x Q)}
\end{figure}

\section{Atividades do Projeto}
\label{metodo3}

\section {Requisitos do Sistema}
\label{req}

>>>>

\begin{figure}[H]
    \centering
    \resizebox{170mm}{!}{\includegraphics{Figuras/19:03/axs2.png}}
    \caption{Cone Jet Classification}
    \label{fig:multi_class_exp}
\end{figure}

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=17cm]{Figuras/19:03/axs1.png}
            \caption{running experiment print screen}
        \end{figure}

@@

        \begin{algorithm}
            \caption{simple controller}\label{alg:simple_controller}
            \begin{algorithmic}
            \Function{controller}{$spray\_mode$}

                \If{$spray\_mode$ = $'Intermittent'$ or $spray\_mode$ = $'Dripping'$}
                    \State \Call{send\_voltage\_command}{$voltage$ + 100}
                \ElsIf{$spray\_mode$ = $'Multi Jet'$ or $spray\_mode$ = $'Corona'$}
                    \State \Call{send\_voltage\_command}{$voltage$ - 100}
                \ElsIf{ $spray\_mode$ = $"Cone Jet"$}
                    \Comment{Keep Stable}
                \EndIf

            \EndFunction
            \end{algorithmic}
        \end{algorithm}

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=15cm]{Figuras/19:03/control_first_results.png}
            \caption{ exp-26-01-2 (V x Q)}
        \end{figure}

    \subsection{Robust Controller}

    \subsection{Fuzzy Controller}

        The fuzzy approach of controller was explored and simulated but not used in the final version of the project.
        This because for this fuzzy approach we need to have the input variables for the fuzzy machine to be fuzzified.
        Which means that to use a fuzzy logic in our controller loop the classification must be fuzzyfied and our classification algorithm was not developed in order to give a classification and its current membership function.

        For that, I tried to fuzzyfi the controller input by the data acquired in the step routine. With the data I mapped the area of each spraying mode according to its potential and fuzzyfied this as shown in the Figure X.

        \begin{multicols}{2}
            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/fuzzyfy_input.png}}
                \caption{Fuzzyfication}
                \label{fig:fuzzy_input}
            \end{figure}

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/defuzzyfy.png}}
                \caption{Defuzzyfication}
                \label{fig:fuzzy_output}
            \end{figure}
        \end{multicols}

        \begin{figure}[H]
            \centering
            \resizebox{80mm}{!}{\includegraphics{Figuras/fuzzy/rules.png}}
            \caption{Fuzzy Rules}
            \label{fig:fuzzy_rules}
        \end{figure}

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test1.png}}
                \caption{Test 1: fuzzy controller}
                \label{fig:fuzzy_test1}
            \end{figure}

            \begin{figure}[H]
                \centering
                \resizebox{90mm}{!}{\includegraphics{Figuras/fuzzy/test2.png}}
                \caption{Test 2: fuzzy controller}
                \label{fig:fuzzy_test2}
            \end{figure}

\section{Atividades do Projeto}
\label{sec:metodo3}

\section {Requisitos do Sistema}
\label{sec:req}
